### 2023-05-06 kutato.tex
Extended results section and fixing grammar issues

>>>>

    \bibitem{pretrained-resnet}
    Xuan Cao, Zhang Chen, Anpei Chen, Xin Chen, Shiying Li, and Jingyi Yu. 2018a.
    \textit{Sparse Photometric 3D Face Reconstruction Guided by Morphable Models. In    IEEE Conference on Computer Vision and Pattern Recognition (CVPR). 4635–4644.}

    \bibitem{regularization-survey}
    Tian, Yingjie, and Yuqi Zhang.
    \textit{A comprehensive survey on regularization strategies in machine learning. Information Fusion 80 (2022): 146-166.}
